Future cosmic microwave background delensing with galaxy surveys

### 2017-12-03 Notes/referee_response.tex

\documentclass[12pt]{amsart}
\usepackage[top=2.5 cm, bottom=2.5 cm, left=1.05in, right=1.05in]{geometry}
%\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
\usepackage[applemac]{inputenc}
\usepackage{amsmath,amssymb} 
% See the ``Article customise'' template for come common customisations
\usepackage{bm}
\usepackage{epsfig}
\usepackage{graphicx,epsfig}
\usepackage{hyperref}
\usepackage{ifthen}
\usepackage [english]{babel}
\usepackage{xstring}
\usepackage[applemac]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{caption}
\captionsetup{justification=centerlast,singlelinecheck=false,font=small,skip=2pt}
% notes to make comment is non-zero if
\newcommand{\al}[1]{\begin{align} #1 \end{align}}

\newcommand{\note}[1]{\textsc{#1}}
	\newcommand{\bR}[1]{{\bm {\mR{#1}}} }

\def\l{\ell}
% For various journals
\newcommand{\apj}{ApJ}
\newcommand{\physrep}{Physics Reports}
\newcommand{\jcap}{JCAP}
\newcommand{\apjl}{ApJL}
\newcommand{\araa}{ARA\&A}
\newcommand{\apjs}{ApJS}
\newcommand{\aap}{A\&A}
\newcommand{\mnras}{MNRAS}
\newcommand{\physrev}{Phys. Rev.}
\newcommand{\physrevlett}{Phys. Rev. Lett.}
\newcommand*\aj{AJ}
%\newcommand*\prd{Phys.~Rev.~D}

\newcommand{\nver}{\hat{\mathbf{n}}}
\newcommand{\cov}{\text{Cov}}
\newcommand{\Nsim}{N_{\text{sim}}}
\newcommand{\relook}[1]{{\textcolor{blue}{\bf #1}}}
%--------- NEW COMMAND STUFF
	\newcommand{\PD}[2]{\dfrac{\partial #1}{\partial #2}}

\def\simlt{\lesssim}
\def\simgt{\gtrsim}
\newcommand{\Omegamzero}{\Omega_{{\rm m,0}}}
\newcommand{\alm}{a_{lm}}
	% * subscript
	\def\rom#1{%
		_{\mathrm{#1}}%
	}%
%\newcommand{\l}{\ell}}

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ben{\begin{equation*}}
\def\een{\end{equation*}}

\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\ban{\begin{eqnarray*}}
\def\ean{\end{eqnarray*}}

\newcommand{\refsec}[1]{section~\ref{sec:#1}}
\newcommand{\reftab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\refeq}[1]{Eq.~(\ref{eqn:#1})}
\newcommand{\refssec}[1]{section~\ref{subsec:#1}}
\newcommand{\reffig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\refFig}[1]{Fig.~\ref{fig:#1}}
	\newcommand{\mR}[1]{\mathrm{#1}}   % mathrm

\definecolor{darkgreen}{cmyk}{0.85,0.2,1.00,0.2}
\definecolor{purple}{cmyk}{0.5,1.0,0,0}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{natbib}
\newcommand{\bx}{{\bf x}}
\newcommand{\bk}{{\bf k}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bP}{{\bf\Psi}}
\newcommand{\bs}{{\bf s}}
\newcommand{\cs}{{\cal S}}
\newcommand{\by}{{\bf y}}
\newcommand{\deltar}{\delta_{\rm recon}}%\def\lcdm{$\Lambda$CDM}
\def\arcsec{$^{\prime\prime}$}
\def\nl{N_\ell}
\def\sl{S_\ell}
\def\ublu{\bl'}
\newcommand{\conv}[2]{\left(\frac{#1}{#2}\right)}
\def\arctanh{\mathop{\rm arctanh}\nolimits}
%\renewcommand{\eqref}[1] {equation $($\ref{#1}$)$}
\newcommand{\comment}[1]{{}}
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\beqn{\begin{eqnarray}}
\def\eeqn{\end{eqnarray}}
\def\a{\alpha}
\def\cl{C_{\ell}}
\def\h{\mathrm{h}}
\def\d{\rmn{d}}
\def\pa{\partial}
\def\deldel#1#2{\frac{\pa{#1}}{\pa{#2}}}
\def\ba{\bm{\alpha}}
\def\fracj#1#2{{\textstyle{#1\over#2}}}
\def\bxi{\bm{\xi}}
\def\half{\frac{1}{2}}
\def\ti{\widetilde}
\def\O{\Omega}
\def\OL{\Omega_\Lambda}
\def\Om{\ensuremath{\Omega_{\mathrm{m}}}}
\def\Ob{\ensuremath{\Omega_{\mathrm{b}}}}
\def\Oc{\ensuremath{\Omega_{\mathrm{CDM}}}}
\def\msol{\ensuremath{M_\odot}}
\def\l{\left}
\def\r{\right}
\def\o{\omega}
\def\gcm{\textrm{g cm$^{-3}$}}
\def\2gcm{\textrm{g cm$^{-2}$}}
\def\Scr{\Sigma_{\mathrm{crit}}}
\def\rcr{\rho_{\mathrm{crit}}}
\def\phidot{\ensuremath{\dot\phi_{\bl,\bl'}}}
\def\ddelta{\ensuremath{\dot\delta}}
\def\modu#1{\l |{#1}\r |}
\def\av#1{\l \langle{#1}\r \rangle}
\def\hmpc{\:{h}^{-1}\mathrm{Mpc}}
\def\th{\Theta}
\def\tth{\tilde\Theta}
\def\sg{\sigma}
\def\Sig{\Sigma}
\def\cf{{\cal F}}
\def\k{\kappa}
\def\P{{P}}
\def\pnl{{P}_{{\!\textrm{\tiny NL}}}}
\def\dnl{\Delta_{\text{\scriptsize NL}}}
\def\kmin{\k_{\mathrm{min}}}
\def\kmax{\k_{\mathrm{max}}}
\def\hires{the \emph{highRes} experiment}
\def\lores{the \emph{lowRes} experiment}
\def\ktot{\k_{\mathrm{tot}}}
\def\hunit{\ensuremath{\mathrm{km}{\mathrm{s}^{-1}} \mathrm{Mpc}^{-1}}}
\def\H0{\ensuremath{\mathrm{H}_0}}
\def\nn{\nonumber}
\def\lin{\mathrm{lin}}
\def\ISW{\mathrm{ISW}}
\def\bl{\bmm{l}}
\def\bL{\bmm{L}}
\def\fsky{f_{\mathrm{sky}}}
\newcommand{\E}[1]{\times 10^{#1}}
\newcommand{\bmm}[1]{{\mathbf{#1}}}
\newcommand{\bsection}[1]

@@

\title{  \scriptsize{Response to Referee for: "Future cosmic microwave background delensing with galaxy surveys"}}
\author{A. Manzotti}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}
\pagestyle{empty}
\maketitle

I want to thank the referee for the very careful review of the paper, and for the comments, corrections, and suggestions that ensued.

We sequentially address all of the points raised below.
While working on this answer, I found a minor bug in the part of the code that plots the CIB kernel in Fig 1 (the CIB kernel peak is slightly shifted). This is fixed now, and it does not affect the results.
\vspace{1.cm}

@@

\begin{enumerate}
\item The abstract is unnecessarily very long and could be considerably
shortened.

\vspace{0.4cm}
I agree.
The abstract length is now reduced to $\sim 80\%$ of its previous length, mainly removing redundancy and quantitative results that can be found easily in the tables while leaving the main general points. I believe it is still a little bit longer than the average but reasonably so.
\vspace{1cm}

@@

\item Putting the lmin-lmax ranges in the tables as well as having the
dashed grey line of Fig. 5 onto Fig 6-7-8 would help the readability
of the paper. 
\vspace{0.4cm}

I agree with the referee on this point. I first thought this could cause a bit of clatter, but the gain in readability is worth the risk.
I added the dashed line to all the figures. The $\ell$ range used for the inflationary constraints is also at the end of each table both for readability and reproducibility. The choice was quite arbitrary tough. We used all the scales available to the instrument. The range where the bulk of the signal to noise is, has been explored in some of the referenced work (\cite{wu:2014,abazajian:2016} etc.) but not here.

@@

\vspace{1cm}
\item Twice in the paper the author writes that lensing is only one of
secondaries producing B-modes, or his writing gives that impression.
It is unclear to me what is meant by that, as far as I know, galactic
foregrounds should be basically the only expected source of worries
for the experiments considered there.

\vspace{0.4cm}

We agree that the phrasing of the sentences where secondary B-modes sources are introduced can be confusing. While it is well known in the field, it is  important to be clear to a broader audience.
For this reason we add this sentence in the introduction:

\vspace{1cm}
\textit{Two main effects produce non-primordial B-modes: the polarized foregrounds from our own galaxy  and the effect of gravitational interactions with large scale structures (LSS). 
This two components needs to be treated with very different techniques and in this work we will focus on the latter (see \cite{remazeilles:2017b} for a review on the former).}

@@

\vspace{1cm}
\item The author introduces sharp cuts to CIB and WISE at $\ell < 100$. Is the
alternative approach of incorporating the foreground content in the
auto spectra of the tracer (E.g. Eq. 17) combination possible ? That
would retain some more of the signal presumably. 
\vspace{0.4cm}

This is indeed a good idea. The real obstacle to that is our current knowledge of foreground spectra. There is not an accurate model for that (at higher scales we use a simple power law). However one might measure that empirically, given a dataset with enough signal to noise on those large scales, by measuring $C^{II}$ and $C^{I\phi}$ directly from the data. Doing that will call everything in the tracer map that does not correlate with $\phi$, "noise". That noise will include foregrounds too. However, it is unclear if eventual dust residual can cause biases in the delensed B-modes (if they correlate with dust contamination in CMB polarizations).
Given the small amount of delensing power for $\ell<100$ the field decided, so far, to cut those in forecasts. Given how much foregrounds are complicated I believed only data would answer this. An exploration of these on simulations is probably beyond the scope of this paper, but very soon future delensing work will need to explore this on real data.

@@

\vspace{1cm}
\item Fig 1 might look confusing at first. The SKA kernel there shows
brilliant overlap with the CMB lensing kernel, but is not the most
powerful tracer. On the other hand, DES for instance has very moderate
overlap but can still achieve very high performance on large scales.
Can the author comment and help the reader make sense of that figure ?

\vspace{0.4cm}
I agree Fig 1 may be a little confusing because it does not tell the entire story. 
The redshift overlap is not the only ingredient for the delensing efficiency. For example, the noise is relevant as well, and this is why for example for S2 experiments CIB can be better than the CMB internal reconstruction even if the latter has a perfect overlap. 
Additionally, not all the redshifts matter at the same level since they correspond to different angular scales (depending on the distance of the tracer) which, as shown by the dashed curves in the figures 5-8, contributes differently.
Showing all of this in one plot is hard.

However, I think Fig 1 tells most of the story. For example, the referee is right that DES is less efficient than SKA in delensing efficiency (16\%) vs (52\%).
Furthermore, I think this figure highlights the central part (the "kernel") that characterize different tracers spectra (using Eq. 2) for people not familiar with it.

I added to the caption a sentence to highlight that the efficiency is not proportional to the overlapping area of this plot because different redshifts contribute differently due to instrumental noise and the geometric properties of the lensing kernel.
\vspace{1cm}

@@

\item Is it clear, as the author claims in IV A with no supporting
evidence, that fixing the cosmology has no impact on the {r,nt}
constraints ? The cosmology fixes the residual B-mode amplitude, which
is unequally important in the delensed vs nominal cases. An slightly
improved discussion would be welcome here.

\vspace{0.4cm}
Note that indeed, as specified in the text, the chosen cosmology \textit{has} an impact on the absolute value of the $r$,$n_{t}$ constraints.
What I claim is that cosmology has almost no impact on, in particular if compared to other uncertainties, is the delensing efficiency (how much these constraints improve), i.e. the ratio $C^{BB}_{\ell}$ nominal/delensed. What matters for the efficiency is the \textit{fraction} of removed power. That depends only on the factor  $1-\rho^2$ where $\rho$ is the correlation factor.
The correlation factor has a very little dependence on cosmology in particular given the tight constraints from Planck on $\Omega_{m}h^2$ and $\sigma_{8}$, and it is expected to be a secondary uncertainty here compared to, for example, the redshift distribution of tracers. Indeed $\rho$ contains $C^{II}$ $C^{I\phi}$, $C^{\phi\phi}$ that are integrals, with slightly different weights in redshift, of the cosmology dependent power spectrum $P(k)$. For this reason, they should scale similarly with cosmology leading to a cancellation in the cosmological dependence of $\rho$.

Testing this intuition is important. For this reason, I run the same pipeline with $10\%$ higher $\Omega h^{2}$, which is almost 40 times more than what Planck constraints \cite{planck-collaboration:2016b}. The efficiency values changes, but by at most $7\%$. Given that the Planck constraints are way tighter I consider this, as expected, a present but subdominant effect. I added a line to the paper to report this test.

@@

%Furthermore, the amplitude of the lensing B-modes (more so given that we do not use the reionization peak in the constraints) scale very simply with cosmology.

\vspace{1cm}

\item The author makes a strong point that survey data should be split
into bins, as this makes the correlation increases by 30\%. I am not
entirely convinced that this is as relevant as claimed. From Fig 4, it
seems that the improvement is fairly limited on the scales that are
relevant for B-mode delensing. Presumably, that is more important for
T or E delensing. The author might want to comment or adapt.

\vspace{0.4cm}
In general, I agree with the point that quoting the improvement in the correlation is not entirely fair because the scales at which that improvement happens is also necessary to understand how much power will be removed.
For this reason, I added in the abstract this quantity too.

Furthermore, while I agree that the improvement would be even more significant for T-E delensing, it is nonetheless also quite important for BB too.
As can be seen in Figure 4 in the paper LSST shows a significant improvement in the correlation with the lensing potential all the way to $\ell\sim 800$. Even for other probes, in general, less powerful, there is still an improvement for example where the contribution to BB (the dashed line peaks at $\ell\sim350$).
Below I am attaching a table that shows the improvement in the BB power removed and constraints on $\sigma(r)$.

@@

In some sense, we assume that either the technique applied in Namikava 2017 or () can work without a significant loss of signal. (put that in the text?s)
Again to test this one needs either real data or full ray tracing simulation for CMB lensing. For example, the deep 100 deg$^{2}$ field measured by SPTPol that can reach a depth of 5-6 muK arcmin with high resolution might be the first dataset where this can be explored.

Following the referee comments, we
\begin{itemize}
\item Make it clear that only CMB S4 will benefit from iterative delensing.
\item Add the level of delensing that is possible to achieve with CMB-S4 if the well tested QE is used instead of the iterative approach. This gives in some sense a range of possible efficiency for CMB S4 experiments.
\end{itemize}

\end{enumerate}

\bibliographystyle{mnrasunsrt}
\bibliography{/Users/alessandromanzotti/Work/Astrophysics/latex_bib/cosmobib,/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/2016/delens100d/delens100d,/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/BIBTEX/spt,
/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/BIBTEX/spt}

### 2017-12-03 Notes/galaxy_delensing.tex
working on referee response

The CMB lensing potential is \textit{the} field that we need in order to reverse the effect of large scale structure and delens the CMB.
However, the lensing potential can also be reconstructed using the CMB itself. In that case, we can treat it as a noisy tracer of the true field. Both the CMB lensing field and its noisy reconstructed counterpart have the same kernel $W^{\kappa}(z)$.
However, when computing the power spectrum of the latter, we need to add a noise component. Given the instrumental noise level and the beam, we can calculate the reconstruction noise $N_{\ell}^{\kappa \kappa}$, and so
\beq\label{eqn:noisekappa}
\cl^{\kappa_\mathrm{rec} \kappa_\mathrm{rec}} = \cl^{\kappa \kappa } +N^{\kappa \kappa}_{\ell}
\eeq
In this work, the level of noise is computed assuming an iterative approach to the CMB lensing reconstruction as described in \cite{smith:2012,hirata:2003}. The iterative approach has not been fully demonstrated on data yet but it is among the major goals of the CMB community (\cite{abazajian:2016}).
Note however that, as pointed out in in \cite{smith:2012,hirata:2003}, this improves the CMB lensing reconstruction compared to a quadratic estimator approach only for CMB-S4 noise levels.

@@

In \refeq{fisher} we are making a few important assumptions. 
First, we are fixing all the cosmological parameters except $\{r,n_{t}\}$. Uncertainties in those will propagate to larger uncertainties in $\{r,n_{t}\}$. While neglecting this will lead to slightly optimistic constraints, it has no significant impact on the estimate of the improvement due to delensing.

@@

%===========================
%===========================
\begin{table}
\caption{$\alpha(r)$: Improvements on $\sigma(r)$ due to delensing for completed and ongoing Stage-2 surveys and Planck lensing reconstruction.
LSS-S2 corresponds to the combination of all the available LSS tracers.
The values in parenthesis in the first column correspond to the fraction of lensing B-mode power removed using each LSS tracer. 
It is defined as $\left<C_{\ell}^{BB,\mathrm{res}}/C_{l}^{BB,\mathrm{lens}}\right>_{4<\ell<100}$.
%\newline
The values in the other columns correspond to ratio of the error before and after delensing for 3 cases: no instrumental noise in the B-mode measurement (but with instrumental noise in the E-mode used to delens) and with instrumental noise for two different values of $r$.}
  \vspace{0.2cm}
  \begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
WISE (8\%)& 1.08& 1.05 & 1.02 \\ \hline
DES (17\%) &1.20 & 1.13  & 1.05 \\ \hline
CIB (30\%) &1.44& 1.26  & 1.10\\ \hline
LSS-S2 (42\%) &1.75& 1.42  & 1.15\\ \hline
CMB Planck (7\%) &1.06 & 1.04  & 1.02 \\ \hline
LSS-S2 +CMB (45\%)& 1.81& 1.45& 1.16  \\ \hline
\end{tabular}
\label{tab:current}
\end{table}
%===========================
%===========================

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ due to delensing for S3 experiments. Here we define LSS-S3 as the combination of S2 LSS tracers (LSS-S2) and DESI. We also use a CMB S3 experiment for the lensing internal reconstruction. See \refsec{S3} for details.}
%The absolute error value of $\sigma(r)$ after delensing for $f_{sky} = $ is $\sigma(r) =$ 
\hspace{2.2cm}
\begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
DESI (11\%) &1.13 & 1.1  & 1.04 \\ \hline
LSS-S3 (45\%) &1.82& 1.59  & 1.18\\ \hline
CMB 3G (56\%) &2.31& 1.9  & 1.23 \\ \hline
LSS-S3+CMB (68\%)& 3.17 & 2.3& 1.30  \\ \hline
\end{tabular}
\label{tab:S3}
\end{table}

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ and $\sigma(n_{t})$ after delensing for S4 experiments. Here we define LSS-S4 as the combination of S3 LSS tracers (LSS-S3) and LSST. We also consider SKA-like radio-continuum surveys. We also use a CMB S4 experiment for the lensing internal reconstruction. The improvement for $\sigma(n_{t})$ is computed for fiducial values $r=0.07$ and $n_t=-r/8$. See \refsec{S4} for details.}
\begin{tabular}{|c | c | c | c| c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ & $\alpha^{n_{t}}_{r=0.07}$ \\ \hline \hline
LSST (51\%) &2.1 & 1.9  & 1.21 & 1.47 \\ \hline
LSS-S4  (59\%) &2.4 & 2.1  & 1.25 & 1.57\\ \hline
SKA (10$\mu$Jy) (53\%) &2.1& 1.9  & 1.22& 1.46\\ \hline
LSS-S4 + SKA (62\%) &2.6 & 2.3  & 1.3& 1.6  \\ \hline
CMB S4 (83\%) & 6.22 & 4.1  & 1.42& 2.3 \\ \hline
LSS-S4+CMB (86\%)& 7.7 & 4.7  & 1.46 & 2.46\\ \hline
\end{tabular}
\label{tab:S4}
\end{table}

@@

\bibliographystyle{mnrasunsrt}
\bibliography{/Users/alessandromanzotti/Work/Astrophysics/latex_bib/cosmobib,/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/2016/delens100d/delens100d,/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/BIBTEX/spt}
%/Users/alessandromanzotti/Work/Astrophysics/delensing/sptpol_papers/BIBTEX/spt}

>>>>

The CMB lensing potential is \textit{the} field that we need in order to reverse the effect of large scale structure and delens the CMB.
However, the lensing potential can also be reconstructed using the CMB itself. In that case, we can treat it as a noisy tracer of the true field. Both the CMB lensing field and its noisy reconstructed counterpart have the same kernel $W^{\kappa}(z)$.
However, when computing the power spectrum of the latter, we need to add a noise component. Given the instrumental noise level and the beam, we can calculate the reconstruction noise $N_{\ell}^{\kappa \kappa}$, and so
\beq\label{eqn:noisekappa}
\cl^{\kappa_\mathrm{rec} \kappa_\mathrm{rec}} = \cl^{\kappa \kappa } +N^{\kappa \kappa}_{\ell}
\eeq
In this work, the level of noise is computed assuming an iterative approach to the CMB lensing reconstruction as described in \cite{smith:2012,hirata:2003}. The iterative approach has not been fully demonstrated on data yet but it is among the major goals of the CMB community (\cite{abazajian:2016}).
Note however that, as pointed out in in \cite{smith:2012,hirata:2003}, this improves the CMB lensing reconstruction compared to a quadratic estimator approach mainly for CMB-S4 noise levels.

@@

In \refeq{fisher} we are making a few important assumptions. 
First, we are fixing all the cosmological parameters except $\{r,n_{t}\}$. Uncertainties in those will propagate to larger uncertainties in $\{r,n_{t}\}$. While neglecting this will lead to slightly optimistic absolute constraints, it has no significant impact on the estimate of the improvement due to delensing. For example, running the same pipeline with $10\%$ higher $\Omega h^{2}$, which is almost 40 times more than what Planck constraints \cite{planck-collaboration:2016b}, change the delensing improvement factors by at most $6-7\%$.

@@

%===========================
%===========================
\begin{table}
\caption{$\alpha(r)$: Improvements on $\sigma(r)$ due to delensing for completed and ongoing Stage-2 surveys and Planck lensing reconstruction.
LSS-S2 corresponds to the combination of all the available LSS tracers.
The values in parenthesis in the first column correspond to the fraction of lensing B-mode power removed using each LSS tracer. 
It is defined as $\left<C_{\ell}^{BB,\mathrm{res}}/C_{l}^{BB,\mathrm{lens}}\right>_{4<\ell<100}$.
%\newline
The values in the other columns correspond to ratio of the error before and after delensing for 3 cases: no instrumental noise in the B-mode measurement (but with instrumental noise in the E-mode used to delens) and with instrumental noise for two different values of $r$. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<500$.}
  \vspace{0.2cm}
  \begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
WISE (8\%)& 1.08& 1.05 & 1.02 \\ \hline
DES (17\%) &1.20 & 1.13  & 1.05 \\ \hline
CIB (30\%) &1.44& 1.26  & 1.10\\ \hline
LSS-S2 (42\%) &1.75& 1.42  & 1.15\\ \hline
CMB Planck (7\%) &1.06 & 1.04  & 1.02 \\ \hline
LSS-S2 +CMB (45\%)& 1.81& 1.45& 1.16  \\ \hline
\end{tabular}
\label{tab:current}
\end{table}
%===========================
%===========================

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ due to delensing for S3 experiments. Here we define LSS-S3 as the combination of S2 LSS tracers (LSS-S2) and DESI. We also use a CMB S3 experiment for the lensing internal reconstruction. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$, see \refsec{S3} for details.}
%The absolute error value of $\sigma(r)$ after delensing for $f_{sky} = $ is $\sigma(r) =$ 
\hspace{2.2cm}
\begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
DESI (11\%) &1.13 & 1.1  & 1.04 \\ \hline
LSS-S3 (45\%) &1.82& 1.59  & 1.18\\ \hline
CMB 3G (56\%) &2.31& 1.9  & 1.23 \\ \hline
LSS-S3+CMB (68\%)& 3.17 & 2.3& 1.30  \\ \hline
\end{tabular}
\label{tab:S3}
\end{table}

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ and $\sigma(n_{t})$ after delensing for S4 experiments. Here we define LSS-S4 as the combination of S3 LSS tracers (LSS-S3) and LSST. We also consider SKA-like radio-continuum surveys. We also use a CMB S4 experiment for the lensing internal reconstruction. The improvement for $\sigma(n_{t})$ is computed for fiducial values $r=0.07$ and $n_t=-r/8$. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$ see \refsec{S4} for details.}
\begin{tabular}{|c | c | c | c| c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ & $\alpha^{n_{t}}_{r=0.07}$ \\ \hline \hline
LSST (51\%) &2.1 & 1.9  & 1.21 & 1.47 \\ \hline
LSS-S4  (59\%) &2.4 & 2.1  & 1.25 & 1.57\\ \hline
SKA (10$\mu$Jy) (53\%) &2.1& 1.9  & 1.22& 1.46\\ \hline
LSS-S4 + SKA (62\%) &2.6 & 2.3  & 1.3& 1.6  \\ \hline
CMB S4 (83\%) & 6.22 & 4.1  & 1.42& 2.3 \\ \hline
LSS-S4+CMB (86\%)& 7.7 & 4.7  & 1.46 & 2.46\\ \hline
\end{tabular}
\label{tab:S4}
\end{table}

@@

\bibliographystyle{mnrasunsrt}
\bibliography{/Users/alessandromanzotti/Work/Astrophysics/latex_bib/cosmobib,/Users/alessandromanzotti/Work/Astrophysics/galaxies_delensing/Notes/spt}
